Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-03-31 paper.qmd
removed latex H from table

# Create the table
kable(notation_df, 
      format = "latex", 
      booktabs = TRUE, escape = FALSE) |>
  kable_styling(latex_options = c("HOLD_position"),
                position = "center", 
                full_width = FALSE, 
                font_size = 12) |>
  row_spec(0, bold = TRUE) |>
  column_spec(1:2, width = c("5cm", "12cm"))
```

>>>>

# Create the table
kable(notation_df, 
      format = "latex", 
      booktabs = TRUE, escape = FALSE) |>
  kable_styling(position = "center", 
                full_width = FALSE, 
                font_size = 12) |>
  row_spec(0, bold = TRUE) |>
  column_spec(1:2, width = c("5cm", "12cm"))
```
